\documentclass[10pt]{article}

% Packages
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{geometry}
\geometry{margin=1in}

\title{Adaptive Reranking for Visual Place Recognition}
\author{}
\date{}

\begin{document}

\maketitle

\begin{table}[t]
\centering
\caption{Comparison of CosPlace baseline, Adaptive Reranking (logistic-regression-based), and Full Reranking across four VPR benchmarks. We report Top-1 accuracy (\%) and reranking time (minutes).}
\label{tab:adaptive_vs_full}

\resizebox{\linewidth}{!}{
\begin{tabular}{lcccc}
\toprule
\textbf{Dataset} & \textbf{CosPlace} & \textbf{Adaptive Rerank} & \textbf{Full Rerank} & \textbf{Time (A / F)} \\
\midrule
SF-XS-test       & 70.0 & 78.0 & \textbf{81.3} & 10 / 39 \\
SVOX-test-sun    & 73.0 & 87.0 & \textbf{90.1} & 9 / 32 \\
SVOX-test-night  & 49.0 & 72.0 & \textbf{73.5} & 17 / 31 \\
Tokyo-test       & 70.0 & 84.0 & \textbf{85.7} & 4 / 12 \\
\bottomrule
\end{tabular}
}
\end{table}

\section{Analysis of Adaptive Reranking}

Table~\ref{tab:adaptive_vs_full} presents the performance of our logistic-regression-based
adaptive reranking module compared to the CosPlace baseline and the full reranking pipeline.

\subsection{Accuracy Improvements}

Adaptive reranking consistently improves over the CosPlace baseline across all datasets.
The gains are substantial:
\begin{itemize}
    \item SF-XS-test: +8.0\%
    \item SVOX-test-sun: +14.0\%
    \item SVOX-test-night: +23.0\%
    \item Tokyo-test: +14.0\%
\end{itemize}

These results demonstrate that even a lightweight learned reranker can correct many of the
baseline retrieval errors, particularly under challenging conditions such as nighttime imagery.

\subsection{Comparison to Full Reranking}

Adaptive reranking recovers the majority of the performance of the full reranking pipeline.
The remaining gap is small:
\begin{itemize}
    \item SF-XS-test: 3.3\% behind full reranking
    \item SVOX-test-sun: 3.1\% behind
    \item SVOX-test-night: 1.5\% behind
    \item Tokyo-test: 1.7\% behind
\end{itemize}

This shows that the logistic regression model captures most of the geometric consistency
signals used by the full reranking stage.

\subsection{Computational Efficiency}

Adaptive reranking is significantly faster than full reranking:
\begin{itemize}
    \item SF-XS-test: 3.9$\times$ faster
    \item SVOX-test-sun: 3.5$\times$ faster
    \item SVOX-test-night: 1.8$\times$ faster
    \item Tokyo-test: 3.0$\times$ faster
\end{itemize}

This makes adaptive reranking suitable for real-time or large-scale VPR deployments where
full reranking is computationally prohibitive.

\subsection{Nighttime Robustness}

The largest relative improvement occurs on SVOX-test-night (+23\%), indicating that the
logistic regression model is particularly effective under severe illumination changes.
This suggests that the reranker learns discriminative geometric cues that remain stable
even when appearance-based descriptors degrade.

\section{Summary}

Overall, adaptive reranking provides an excellent trade-off between accuracy and
computational cost. It consistently boosts Top-1 accuracy over the CosPlace baseline while
remaining significantly faster than full reranking. These results demonstrate that a simple
learned reranker can approximate the performance of a full geometric verification pipeline
at a fraction of the computational cost.

\end{document}